### 2021-05-26 LaTeX-ACM/sections/paper.tex
adding cm citations
randomz

% JC: Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.

@@

We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce gas costs by more than 99.9\% savings. While roll-ups are not fully on-chain and introduce new network participants, the roll-up architecture is still concerning to regulators because the participants (called validators) are not directly reachable by users; they only watch the Ethereum state and interact directly with Ethereum.

@@

\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fueled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees. By contrast, an order book requires no upfront inventory and trading fees are optional. Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.

@@

Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market. One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price. Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

\cm is proof of concept code. We try to simplify the design at every step to make it an extensible base class but still functional without any extensions. A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). Later in Section~\ref{sec:close}, we discuss the options for who closes/reopens the market. We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}. As markets are relatively short-lived, orders simply expire when the market call period ends.

@@

@@

(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction; (ii) in an \emph{insertion attack}, Mallory similarly inserts a transaction before Alice and ensures Alice's transaction is the next to run, and (iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time. Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's. Later in Section~\ref{sec:frontarb}, we discuss a third kind of participant: sequencers.

@@

When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order. In \cm, tokens are assumed to be divisible. We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).

\paragraph{Evaluation.} A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work. Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and countermeasures could take a few blocks to select~\cite{boneh2018verifiable}).

@@

\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes \textblue{Should we refer to the new front-running section here???} ). Also, cancellations have a performance impact. Canceled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

@@

\paragraph{Evaluation.} \textblue{???}
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

\textblue{JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.}

As a simple base class, \cm is a one-shot market. However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run. Modifiers can enforce when the market operates openly (collecting orders) and when close can be run. In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).

@@

\paragraph{Evaluation.} \textblue{???}

@@

\paragraph{Evaluation.} \textblue{??}

@@

We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX). We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

@@

 \subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted). We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0x18BF65069Fdaed79f8BDB0B6EDa87d5cc46F6E28}{[explorer5.offchainlabs.com]}.

>>>>

% Final camera-ready
% JC: Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.

@@

We also speculate that Ethereum is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum} which reduce the gas costs of \cm by more than 99.9\%. While roll-ups are not fully on-chain and introduce new network participants, the roll-up architecture is still concerning to regulators because the participants (called validators) are not directly reachable by users; they only watch the Ethereum state and interact directly with Ethereum.

@@

\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees. By contrast, an order book requires no upfront inventory and trading fees are optional. Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.

@@

Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market. One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price. Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in using them to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

\cm is proof of concept code and an extensible base class that is still functional without any extensions. A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). Later in Section~\ref{sec:close}, we discuss the options for who closes/reopens the market. We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}. As markets are relatively short-lived, orders simply expire when the market call period ends.

@@

In an \emph{insertion attack}, Mallory learns of a transaction from Alice, arranges for her transaction to run first with the purpose of Alice's transaction being the next transaction to run. For example, if Alice was

@@

(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction;

(iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time. Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's. Later in Section~\ref{sec:frontarb}, we discuss a third kind of participant: sequencers.

@@

When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order. A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work. Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped, (2) bids could be prioritized based on time, or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}).

\paragraph{Evaluation.} We avoid (1) which is fair but not market efficient. We note the conditions under which pro rata allocation fails (\ie non-divisible assets, an exact tie on price, and part of the final allocation) are improbable. In \cm, tokens are assumed to be divisible but we otherwise default to (2). This means insertion front-running attacks are possible for this corner case. However if these attacks proved to be a problem in practice, (3) is a better solution with one main drawback: on-chain sources of `randomness' are generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs}, countermeasures can take a few blocks to select~\cite{boneh2018verifiable}).

@@

\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes. Also, cancellations have a performance impact. Canceled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. %A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

@@

@@

\cm is a one-shot market. However it can be extended to reopen with a clean order book after \texttt{closeMarket()} is run. Modifiers can enforce when the market operates openly (collecting orders) and when close can be run. In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).

@@

@@

@@

We consider an alternative design for \cm that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

% For background information on different types of roll-ups, please see Appendix~\ref{app:rollup}

@@
